manuscript_outline

### 2025-05-27 docs/manuscript/paper.Rmd
fix phylogenetic example

```{r, fig.align = 'center', fig.cap="Custom hatch timing models developed for four North American frog species. Models are parameterized from Moore 1939 and phenology is predicted using a randomly generated temperature regime with mean 16 °C."}

@@

set.seed(123)
temperature_data <- data.frame(temperatures = sort(rnorm(30, mean = 16, sd =2.5)),
                               dates = seq(ymd("2000-04-01"), ymd("2000-04-30"), by = "days"))

@@

froggy_hatch <- map(froggy_mods,
                    predict_phenology,
                    data = temperature_data,
                    dates = dates,
                    temperature = temperatures,
                    spawn.date = "2000-04-01") |>
  map_dbl("days_to_develop") |>
  sort(decreasing = TRUE) |>
  tibble()

@@

froggy_hatch <- froggy_hatch |>
  mutate(start = ymd("2000-04-01"),
         stop = start + days_to_develop,
         species = c("Green Frog", "Pickerel Frog", "Northern Leopard Frog", "Wood Frog"),
         index = seq(20.5,17.5, by = -1))

@@

p2.1
```

>>>>

Pic labels are wrong, check

```{r, fig.height= 4.5 , fig.align = 'center', fig.cap="Custom hatch timing models developed for four North American frog species. Models are parameterized from Moore 1939 and phenology is predicted using a randomly generated temperature regime with mean 16 °C (Panel A). Panel B shows the effective values for different mean daily temperatures for each species, which are effectively species-specific linearized developmental reaction norms."}

@@

### Figure A Code
set.seed(123)
temperature_data <- data.frame(temperatures = sort(rnorm(30, mean = 16, sd =2.5)),
                               dates = seq(ymd("2000-04-01"), ymd("2000-04-30"), by = "days"))

@@

froggy_hatch <- map(froggy_mods,
                    predict_phenology,
                    data = temperature_data,
                    dates = dates,
                    temperature = temperatures,
                    spawn.date = "2000-04-01") |>
  map_dbl("days_to_develop") |> 
  tibble()

@@

froggy_hatch <- froggy_hatch |> 
    mutate(species = c("Wood Frog", "Pickerel Frog", 
                       "Green Frog","Northern Leopard Frog" )) |> 
  arrange(desc(days_to_develop))

froggy_hatch <- froggy_hatch |>
  mutate(start = ymd("2000-04-01"),
         stop = start + days_to_develop,
         index = seq(20.5,17.5, by = -1))

@@

### Figure B code

temps <- c(6:20)
species = species = c("Wood Frog", "Pickerel Frog", 
                       "Green Frog","Northern Leopard Frog" )
ef_vals <- NULL

for( m in 1:length(froggy_mods)){
  mod = froggy_mods[m]
  frog = species[m]

for (x in temps) {
  ef <- eval(parse(text = mod))
  temp_df <- data.frame(temperature = x, 
                        effective_value = ef, 
                        frog_species = frog)
  ef_vals <- rbind(ef_vals, temp_df)

  }
}

data_2 <- tibble(temperature = c(0:20), effective_value = seq(0, 0.20, by = 0.01))

p2.2 <- ef_vals |> tibble() |> 
  ggplot(aes(x = temperature, y = effective_value, color = frog_species)) +
  geom_line() +
  geom_point() +
  geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily Average Temperature (°C)", y = "Effective Value") +
  scale_color_manual(values = c("darkolivegreen4","deepskyblue4", "grey23",  "purple4"), name = "Species") +
  theme_classic() +
  theme(legend.position = "none")

p2.1 + p2.2 + plot_annotation(tag_levels = 'A')
```
